Spatial Analysis

### 2021-06-09 Scripts/spatial_analisis.Rmd
created function to run and save tis

  # print(paste(yr))

  data <- input_data %>% 
    filter(year == yr,
           spp == taxa,
           region == reg
    ) %>% 
    filter(wtcpue > 0)

    if(nrow(data) == 0){
      return(tibble())
    }else{

@@

@@

# taxa
spp <- "Centropristis striata"

@@

@@

# Simple for-loop for running both regions (seasons)
for(r in 1:2){

  partial_df <- bind_rows(
    lapply(years,tis,input_data = ocean_data, grid = grid, taxa = spp, reg = regions[r])
  )

>>>>

  # --------------- #
  # Testing
  # print(paste(yr))
  # yr = 1976
  # --------------- #

  # Filter data
  data <- input_data %>% 
    filter(year == yr,
           spp == taxa,
           region == reg
    ) %>% 
    # Average duplicated hauls in the same spot
    group_by(region,year,spp,lat,lon) %>%
    summarise_at(vars(wtcpue),
                 mean,na.rm = T) %>%
    filter(wtcpue > 0)

  # Only interpolate cases where there is more than 3 rows
  # Marked by the function 
    if(nrow(data) <= 3){
      fit_tin <- tibble()
    }else{

@@

# Test me
# Needs variables in Control panel
# Test no data: "Alosa aestivalis", reg = "Northeast US Fall", yr = 1974 
tis(input_data = ocean_data, grid = grid_eez_df, taxa = spp[1], reg = "Northeast US Fall", yr = 1974)

### Run function

```{r interpol_run_fun, eval = T, echo = T}

run_tis <- function(input_data, grid, years, taxa, reg){

  # Run tis for species and surveys
  for(r in 1:2){

    partial_df <- bind_rows(
      lapply(years,tis,input_data = ocean_data, grid = grid_eez_df, taxa = taxa, reg = regions[r])
    )

  # ----------------------- #
  # Save dataset per species
  # ----------------------- #

  # Set file name
  name <- paste0("tif_",str_replace(taxa," ","_"),".csv")

  # Set path name
  save_path <- my_path("R","Partial/Interpolation")

  # Set complete path
  save_name <- paste0(save_path,name)

  # Create folder if it does not exist
  if(file.exists(save_path) == F){
    dir.create(save_path)
  }

  #  Save file
  write_csv(historic_tif,save_name)

@@

@@

# taxa
# spp <- "Centropristis striata"

spp <- ocean_data %>% 
  filter(region %in% regions,
         spp != "NA") %>% 
  pull(spp) %>% 
  unique()

@@

# # Simple for-loop for running both regions (seasons)
# for(r in 1:2){
#   
#   partial_df <- bind_rows(
#     lapply(years,tis,input_data = ocean_data, grid = grid, taxa = spp, reg = regions[r])
#   )
#   
#   if(r == 1){
#     historic_tif <- partial_df
#   }else{
#     historic_tif <- bind_rows(historic_tif,partial_df)
#   }
#   
# }

# Run for one species
    run_tis(input_data = ocean_data, grid = grid_eez_df, taxa = "Centropristis striata", years = years, reg = regions)

# Run for multiple species
    run_tis(input_data = ocean_data, grid = grid_eez_df, taxa = spp[1], years = years, reg = regions)
